Compare scANVI and SingleR annotations

### 2025-08-14 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/scanvi-singler-comparison.Rmd
Update analyses/cell-type-neuroblastoma-04/exploratory-notebooks/scanvi-singler-comparison.Rmd
Co-authored-by: Ally Hawkins <54039191+allyhawkins@users.noreply.github.com>

Across libraries, the median posterior probability is always exceptionally high at which suggests `scANVI` confidence is roughly the same across libraries.

>>>>

Across libraries, the median posterior probability is always exceptionally high which suggests `scANVI` confidence is roughly the same across libraries.
